Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-04-20 Paper/Manuscript.tex
Various modifications in paper

\author{Lars Nonboe Andersen}
\email{lars.nonboe.andersen@kongsberg.com}
\affiliation{Kongsberg Maritime AS, Strandpromenaden 50, 3191, Horten, Norway}

@@

The objective of this paper and associated code is to present a systematic and comprehensive description of the data processing steps for calibrated broadband echosounder data. The steps include pulse compression, target strength as a function of frequency [TS(f)], and volume backscattering strength as a function of frequency [Sv(f)]. The intention is that the code will be used to validate implementations in various echosounders and post processing software, provide a starting point for further developing signal processing, and serve as a learning resource for broadbanded acoustic data processing. We also note that the processing equations and methodology presented in this paper are similar to version 1.12.4 and earlier of the Simrad EK80 software.

@@

\subsection{Accompanying code}
The code accompanying this paper is written in Python and is available as supplementary materials. All processing steps with respective figures in the paper can be reproduced by running main script (Main.py). Without loss of generality, we use the Simrad EK80 as an example since it is currently the most used broadband echosounder in the marine ecosystem acoustics field. By presenting the design goals, implementation details, and recommended procedures and processing required to obtain quantitative broadband data, the authors hope to encourage and facilitate the realistic use of broadband signals in marine ecosystem acoustics.

@@

In the example a linear sweep enveloped by a Hann function is implemented (Fig.~\ref{fi:ytx}). This is found in the class \verb|Calculation.generateIdealWindowedTransmitSignal|, where the parameters are the initial frequency, the final frequency, the pulse duration, the sampling rate, and the proportion of the signal that is tapered in each end, respectively. A tapering of 0 and .5 indicates no tapering and tapering across the whole signal, respectively.
\begin{figure}
\includegraphics[width=16cm]{Fig_ytx}
\caption{\label{fi:ytx} Ideal and enveloped transmit pulse between 34 kHz to 45 kHz with a slope of 0.057, as implemented in the EK80. The orange curve illustrate the effect of setting the slope to 0.5.}
\end{figure}

@@

The contribution includes all the minor details required for the processing steps to work in practice. This includes steps well founded in the literature as well as practical and more ad-hoc choices, and a few examples of such choices follows. How to handle gaps in the calibration data, the choice of transmit pulse including tapering, calculation of efficient pulse duration, and decimation factors and filtering are examples of such choices. When convolving the received signal with the transmit pulse, there are various approaches to handle edge cases, and, in our implementation, we simply chose to remove the edge cases. We have also assumed a four-sector transducer, and the code must be adapted to other beam configurations if other configurations are needed. The signal processing also assumes a matched load impedance for the transducer and transceiver. Our objective is not to provide an evaluation of these choices, but to serve as a reference implementation when benchmarking the choices.

>>>>

\author{Lars Nonboe Andersen}
\email{lars.nonboe.andersen@km.kongsberg.com}
\affiliation{Kongsberg Maritime AS, Strandpromenaden 50, 3191, Horten, Norway}

@@

The objective of this paper and associated code is to present a systematic and comprehensive description of the data processing steps for calibrated broadband echosounder data. The steps include pulse compression, target strength as a function of frequency [TS(f)], and volume backscattering strength as a function of frequency [Sv(f)]. The intention is that the code will be used to validate implementations in various relevant data processing software, provide a starting point for further developing signal processing, and serve as a learning resource for broadbanded acoustic data processing. We also note that the processing equations and methodology presented in this paper are similar to version 1.12.4 and earlier of the Simrad EK80 software.

@@

\subsection{Accompanying code}
The code accompanying this paper is written in Python and is available as supplementary materials. All processing steps with respective figures in the paper can be reproduced by running the main scripts (TSf.py and Svf.py). Without loss of generality, we use the Simrad EK80 as an example since it is currently the most used broadband echosounder in the marine ecosystem acoustics field. By presenting the design goals, implementation details, and recommended procedures and processing required to obtain quantitative broadband data, the authors hope to encourage and facilitate the realistic use of broadband signals in marine ecosystem acoustics.

@@

In the example a linear sweep enveloped by a Hann function is implemented (Fig.~\ref{fi:ytx}), where the parameters are the initial frequency, the final frequency, the pulse duration, the sampling rate, and the proportion of the signal that is tapered in each end, respectively. A tapering of 0 and .5 indicates no tapering and tapering across the whole signal, respectively.
\begin{figure}
\includegraphics[width=16cm]{Fig_ytx}
\caption{\label{fi:ytx} Ideal and enveloped transmit pulse between 34 kHz to 45 kHz with a slope of 0.057, as implemented in the EK80. The orange curve illustrates the effect of setting the slope to 0.5.}
\end{figure}

@@

The contribution includes all the minor details required for the processing steps to work in practice. This includes steps well founded in the literature as well as practical and more ad-hoc choices, and a few examples of such choices follows. How to handle gaps in the calibration data, the choice of transmit pulse including tapering, calculation of efficient pulse duration, and decimation factors and filtering are examples of such choices. When convolving the received signal with the transmit pulse, there are various approaches to handle edge cases, and, in our implementation, we simply chose to remove the edge cases. We have also assumed a four-sector transducer, and the code must be adapted to other beam configurations if other configurations are needed. When estimating $\ts(\freqsym)$ and $\sv(\freqsym)$ the resolution and accuracy will depend on the length $\ndft$ of the Fourier transform and the actual choice will be a compromise between accuracy and computational speed. Our objective is not to provide an evaluation of all these choices, but to serve as a reference implementation when benchmarking the choices.
